Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-27 manuscript/manuscript.tex
adding missing reference to fig.2a [ci skip]

For the remainder of this manuscript we will walk through the first notebook (00). In notebook 00 we analyze a dataset of the Trp-Leu-Ala-Leu-Leu pentapeptide, consisting of $25$ independent MD trajectories conducted in implicit solvent with frames saved at an interval of $0.1$~ns. We present the results obtained in the notebook, thereby providing an example of how results generated using PyEMMA can be integrated into research publications.
The figures that will be displayed in the following are created in the showcase notebook (00) and can be easily reproduced.

>>>>

For the remainder of this manuscript we will walk through the first notebook (00). In notebook 00 we analyze a dataset of the Trp-Leu-Ala-Leu-Leu pentapeptide (Fig.~\ref{fig:io-to-ck}a), consisting of $25$ independent MD trajectories conducted in implicit solvent with frames saved at an interval of $0.1$~ns. We present the results obtained in the notebook, thereby providing an example of how results generated using PyEMMA can be integrated into research publications.
The figures that will be displayed in the following are created in the showcase notebook (00) and can be easily reproduced.
